Hierarchical Model Self-Assessment
========================================================

Download the Gasch yeast heat shock experiment from Bioconductor

```{r}
source("http://bioconductor.org/biocLite.R")
biocLite("gaschYHS")
library(gaschYHS)
data(gaschYHS)
e = gaschYHS

#Subset to the first 8 samples, and remove genes with any NA values:
anyNA = function(x) any(is.na(x))
e = e[,1:8]
e = e[!apply(exprs(e), 1, anyNA),]
```

This subset of samples contains already-normalized gene expression measurements for yeast after a heat shock, at the following times: 5, 10, 15, 20, 30, 40, 60, 80 minutes. We want to contrast the early response (up to 30 minutes) to the later response.

We will perform a simple test first, dividing the samples into two groups: the first 5 samples and the last 3 samples:

condition = factor(rep(1:2,c(5,3)))

Run a limma analysis on this dataset, looking for the differences of the second group over the first group.

Inspect the top genes using topTable (use the default sorting). What is the t-statistic for the gene YDR171W encoding heat shock protein?

```{r}
library(limma)
condition = factor(rep(1:2,c(5,3)))
fit <- lmFit(e, design=model.matrix(~ condition))
colnames(coef(fit))
fit <- eBayes(fit)
tt <- topTable(fit, coef=2)
tt
```

Continue working with the same object e as defined above.

In the previous question, we did not make use of the quantitative time information we have, which is stored in pData(e)$time. Now suppose we want to measure which genes rise and fall with time in the first 5 samples:

e = e[,1:5]

time = pData(e)$time

Specify a model matrix with a quadratic dependence on time using the I() function to perform the mathematic operation of squaring:

design = model.matrix(~ time + I(time^2))

Run a limma analysis to find genes which change according to a quadratic pattern over minutes.

Use topTable() to find the 10 top ranked genes for the effect of time and time^2. Hint: this is accomplished by specifying coef=2:3 to topTable. (Use the default sorting, which is by the F-statistic)

What is the F-statistic for the gene YGR211W?

```{r}
e = e[,1:5]

time = pData(e)$time

# design = model.matrix(~ time + I(time^2))

fit2 = fit <- lmFit(e, model.matrix(~ time + I(time^2)))
colnames(coef(fit2))
fit2 <- eBayes(fit2)
tt2 <- topTable(fit2, coef=2:3)
tt2
```

