Week 3 Inference Assessment
==========================================

# Question 1:

We obtain gene expression data for one gene from several mice from each of two strains. We perform a t-test for a difference in average between the two strains and obtain a p-value of 0.06. What does this mean?

### Answer: If we assume there is no difference, the probablyility of a t-statistic being as large or larger than what we observed is 0.06.

# Question 2:

To obtain the p-value above we used the central limit approximation. Suppose we don't wan to assume this asymptotic result holds. What else can we do to obtain a p-value?

### Answer: Perform a permutation test

# Question 3:

Assume we have 10 independent random variables that follow the normal distribution with average=0 and sd=1. We want to compute the median of the 10 random variables. The median of the 10 random variables is

### Answer: a random variable

# Question 4:

Perform a Monte Carlo simulation by repeating the above (computing the median of 10 normally distributed numbers with average=0 and sd=1) 1,000 times. ( Hint: use the R functions rnorm() and replicate() ) You now have 1,000 medians. The standard deviation of these 1,000 numbers is likely to be between

Work:

```{r}
# rnorm(10,0,1) -> n=10, mean=0, sd=1, this is also default, could do rnorm(10)

dat <- replicate(1000, rnorm(10, 0, 1))
sd(dat)

```

### Answer 0.3 - 0.4

# Question 5:

What best approximates the distribution of 1,000 medians of 10 random normal variables?

Work:

```{r}
hist(dat)
qqnorm(dat)
```

### Answer: Normal Distribution

# Question 6:

If we are tossing a die and adding up the number of sixes we see. The following statements are all true, but only one of them is a result of the Central Limit Theorem. Pick the statement that follows from the Central Limit Theorem. If we toss 120 die,

### Answer: The number of sixes will approximately follow a normal distribution

Explanation:
The Central Limit Theorem tells us about the distribution of the sum of independent and identically distributed random variables, and that this distribution tends to a normal distribution. It is not related to the fact that the expected number of sixes is 20, or that the expected ratio is 1/6.